NN_Accel_Heading

### 2024-03-15 Fish Data Analysis/NN_Accel_Heading.qmd
Working on subset of angles

single_comp_data <- na.omit(single_comp_data)

@@

fish_comp_data <- na.omit(fish_comp_data)

@@

min_dist <- 0.75 #sd*0.5
max_dist <- 3 #sd*1.5

@@

@@

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
  geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
                  ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
                  fill = interaction(Ablation, Darkness, sep =", ")),
              alpha = 0.25, colour = NA)+
  theme_classic() +
  ylim(-100,100) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+ 
  guides(fill = FALSE)

>>>>

@@

@@

min_dist <- 3 #sd*0.5
max_dist <- 100 #sd*1.5

@@

Kolmogorov–Smirnov around 90 degrees

perp_angle_df <- fish_comp_data %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105)) %>% filter(Distance >= 2 & Distance <= 100) %>% filter(Flow == "Still Water")

single_fish_df <- perp_angle_df %>% filter(Darkness == "Single" & Ablation == "Single")
LNDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "No Ablation")
LYDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "Ablated")
LNDY_fish_df <- perp_angle_df %>% filter(Darkness == "Dark" & Ablation == "No Ablation")
LYDY_fish_df <- perp_angle_df %>% filter(Darkness == "Dark" & Ablation == "Ablated")

LNDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDN_fish_df$Fish1_Yaw_Heading_PS)
LYDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDN_fish_df$Fish1_Yaw_Heading_PS)
LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDY_fish_df$Fish1_Yaw_Heading_PS)
LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDY_fish_df$Fish1_Yaw_Heading_PS)

p.adjust(c(LNDN_KS$p.value,LYDN_KS$p.value,LNDY_KS$p.value,LNDY_KS$p.value))

# perp_model <- aov(Fish1_Yaw_Heading_PS ~ Darkness*Ablation, data = perp_angle_df)
# Anova(perp_model)
# TukeyHSD(perp_model)

ggplot(perp_angle_df, aes(x = Flow_Ablation_Darkness, y = Fish1_Yaw_Heading_PS,
                          fill = Flow_Ablation_Darkness, color = Flow_Ablation_Darkness))+
  stat_dots(side = "both", binwidth = unit(0.01, "npc")) +
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  theme_classic()+
  ggtitle("Heading per Second, 2 to 100 BL, 75 to 100 Degrees")

@@

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
  # geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
  #                 ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
  #                 fill = interaction(Ablation, Darkness, sep =", ")),
  #             alpha = 0.25, colour = NA)+
  theme_classic() +
  ylim(-100,100) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+ 
  guides(fill = FALSE)
